### 2013-09-18 chi2014/method.tex
Pass through the method section

\section{Method}

In order to develop models and test hypotheses, it was necessary to establish a significant corpus of brainstorming data data. Over the course of four months we repeatedly collected responses to brainstorming tasks.

Participants were recruited from Amazon's \emph{Mechanical Turk} \cite{_amazon_????}, and were restricted to residents of the United States for a baseline expectation of english language comprehension and cultural familiarity. Mechanical Turk is an online marketplace in which members receive financial reward for completing \emph{Human Intelligence Tasks}, or HITs.

HITs were placed on the marketplace asking for a variable \emph{number of ideas}, with proportional rewards. These conditions were : 5 ideas (with a corresponding reward of \$0.18 USD), 10 ideas (\$0.35), 20 (\$0.70), 50 (\$1.75), 75 (\$2.65), and 100 (\$3.50).

This served as the independent variable in all data gathering. It must be stated that under normal brainstorming conditions, participants are asked to generate as many ideas as possible within a fixed time frame, instead of a fixed number. We excluded such a condition for two reasons. First, it is practice in crowd creativity tasks to solicit a fixed number of ideas (e.g. Yu and Nickerson \cite{yu_cooks_2011}). Secondly, we piloted asking respondants for "as many ideas as possible" in a generous time frame. Over N respondents, we received a mean of N ideas (std N), despite giving a financial of \$\$\$\$. This suggested a propensity to "game the system", a behaviour we wanted to exclude.

While the brainstorming question was manipulated in pilot studies, it was fixed for the data reported on in this paper:

\begin{itemize}
\item \textbf{MP3}

Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may \emph{not} have displays. Be as specific as possible in your descriptions.
\end{itemize}

This problem was selected for three qualities:

\begin{enumerate}
\item It requires creativity to resolve. Obvious answers do not satisfy the problem.
\item Mechanical Turk participants have the expertise to solve the problem.
\item It has an associated success metric.
\end{enumerate}

Workers choose which \emph{number of ideas} condition to participate in, thus self-selection bias is a reasonable concern. However, this bias is also present in real-world HIT choice behaviour.

Upon accepting a HIT, participants were asked to give consent and informed that they could leave the study at any point without financial consequences. Under normal conditions, the participants would be expected to complete all responses to receive compensation.

Should we be dropping these runs, or at least testing they don't have an affect?

\subsection{Task}

The brainstorming task is a form in a standard web browser. Participants are presented with a brief overview of the tenets of brainstorming, are presented a problem, and must enter some number of ideas to resolve the problem within an 18 hour period.

At the beginning of the form is a brief introduction to brainstorming, with a paraphrase of Osborne's four rules of brainstorming \cite{osborn_applied_1957}. These rules were manipulated to make sense within the constraints nominal brainstorming over the web medium. The rules, as displayed to the participants:

@@

The brainstorming problem is below this, followed by a series of text entry inputs numbered through to the total number of ideas requested. Figure X (FIG) is an example of a typical task. We place a larger free text area at the bottom of the list where participants could enter any additional ideas.

\subsubsection{Data Collected}

In total, 161 HITs were complteed by 146 distinct participants, for a total of 3007 responses. A breakdown of responses across conditions is given in table TAB. In cases when a single participant participated in multiple conditions, all HITs after the first were dropped for subsequent analysis.

@@

HITs were augmented with JavaScript to collect data in addition to brainstorming responses. For each response, we collected the time of the first activation and last de-activation of the corresponding form element. We collected the time the HIT was accepted and the time it was submitted. To uniquely identify participants, we computed a hash of their Mechanical Turk worker ID. A hash was used to protect privacy after data release.

\subsection{Terminology}

To facilitate discussion, we introduce terms here that we will use throughout the rest of the paper.

An \emph{instance} is a single solution by a single participant to a brainstorming question. Alternatively, an instance may be thought of as the text entered into a single field in the task form. For example, figure~\ref{fig:sample_instances} gives four \emph{instances} from the data set.

@@

A \emph{brainstorming run}, or \emph{run}, is the temporally-ordered series of instances that were received in a single HIT by a single user. As stated above, after dropping repeat data, all brainstorming runs were completed by distinct participants.

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, and all instances in the same idea should be paraphrases of one another. In Figure FIG, "Storage Container" and "Small Storage Box" belong to the same \emph{idea}. However, "Coin Storage" does not belong to the same idea, as it contains additional information.

Despite this, it is clear the ideas have some commonality. It is desireable to encode this relationship. To that end, we propose a hierarchical clustering of ideas in \emph{category trees}. In a category tree, ideas act as nodes. Each idea may have 0 or 1 parent idea (only the root has 0) and 0 or more child ideas. An example category tree for the instances in Figure FIG is given in Figure FIG.

@@

If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B: all instances in A are are suitably general to encompass all instances in B. This hierarchical clustering allows us to classify ideas as simultaneously different in solution stragy but different in solution details.

We further distinguish category trees into \emph{singleton} and \emph{non-singleton} category trees. A singleton category tree is composed of only one idea node, the root. A non-singleton category tree has at least two idea nodes. We introduce non-singleton category trees as correspondents to the images in Nisjstad and Stroebe's SIAM model \cite{nijstad_how_2006}. On SIAM, the idea generation process is represented by a series of images activations within which idea production occurs. Non-singleton trees by definition represent strategies that have been produced in at least two distinct ways.

The \emph{idea forest} is the collection of all category trees. Different trees in the forest have no particular relationship.

\subsection{Clustering}

In addition to the notion of an idea forest, we also propose a clustering algorithm driven by human intelligence to create the data structure. The algorithm is described in Figure~\ref{fig:cluseringalg}. Instances are added one at a time to the existing idea forest. In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

\begin{figure*}[ht]
\small
\begin{verbatim}
for each instance:
  idea_node = new node including instance
  current_node = root of forest
  do:
    best_match = max_similarity(idea_node, current_node.children)

    if best_match.similarity is low or current_node has no children:
      insert idea_node under current_node
      exit do
    else:
      if coverage(idea_node, best_match) == coverage(best_match, idea_node) == high:
        merge idea_node, best_match
        exit do
      else if coverage(idea_node, best_match) == coverage(best_match, idea_node) == low:
        new_parent = new artifical idea node
        insert best_match, idea_node under new_parent
        insert new_parent under current_node
        exit do
      else if coverage(idea_node, best_match) > coverage(best_match, idea_node):
        replace best_match with idea_node in tree
        current_node = idea_node
        idea_node = best_match
      else:
        current_node = best_match
\end{verbatim}
\caption{Manual clustering algorithm}
\label{fig:cluseringalg}
\end{figure*}

The clustering algorithm relies on the human intelligence of the researcher for three key decisions:

\subsubsection{Similarity}
Two nodes a and b have high similarity if they solve the problem in the same way, and low similarity if their solutions have no common themes. For example, in Figure FIG, "Small Storage Box" and "Travel Jewelry Case" have high similarity, as they both solve the problem of using a broken MP3 player by using it to reflect light.

\subsubsection{Coverage}
A node a has high coverage of a node b if the problem solution in a is equal to or an abstraction of the problem solution in b. Coverage is not commutative. To return to the example, "Small Storage Box" has high coverage of "Travel Jewelry Case", as the latter is a just a specific use for the former. On the other hand, the latter idea has low coverage of the former.

\subsubsection{Artificial Ideas}
Occasionally, two nodes have high similarity but no coverage. For example, "Coin Storage" and "Travel Jewelry Case" use the MP3 player in the same way, but neither is a generalization of the other. In this case, the algorithm appeals to the human coder to provide a lable for a new idea that is a generalization of both.

The primary author followed the algorithm to cluster the 3007 response instances into ideas and trees.

>>>>

\section{Method}
In this section, we describe our process of recruiting and remunerating participants, the brainstorming question selected, and the user interface provided the worker. We then describe the data collected, and our method of organizing it into a hierarchical cluster.

\subsection{Recruitment and Remuneration}
To study brainstorming in a crowd environment, we published brainstorming HITs (human intelligence tasks) on Amazon's Mechanical Turk. We restricted our worker pool to residents of the United States to increase the chances of English language comprehension and a shared cultural background. No other screening was performed on workers.

HITs were placed on the marketplace asking for 5, 10, 20, 50, 75, 100, or an unlimited number of ideas for a brainstorming problem. We paid a fixed amount per HIT, computed at a rate of approximately 3.5 cents per idea requested, yielding reward amounts of 18 cents (5), 35 cents (10), 70 cents (20), \$1.75 (50), \$2.65 (75), and \$3.50 (100). For the unlimited condition, we offered \$1.75, pricing it the same as the 50 ideas condition. HITs were advertised with the number of responses requested. Workers had 18 hours to submit the HIT once accepted.

\subsection{Brainstorming Question}
In conducting this research, we tested several brainstorming questions, including classic brainstorming questions (e.g., ``provide alternative uses for a mop''), a request to brainstorm factors that influence weight gain and weight loss, and more goal-oriented questions, such as one requesting people to brainstorm ways to raise funds for a charity. Ultimately, we found the goal-oriented brainstorming questions to be the most compelling since they reflect what we believe would be real-world uses of brainstorming on Mechanical Turk.

The final brainstorming question we chose for this work is the following:

TODO: Indent, italicize this:
Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may \emph{not} have displays. Be as specific as possible in your descriptions.

%This served as the independent variable in all data gathering. It must be stated that under normal brainstorming conditions, participants are asked to generate as many ideas as possible within a fixed time frame, instead of a fixed number. We excluded such a condition for two reasons. First, it is practice in crowd creativity tasks to solicit a fixed number of ideas (e.g. Yu and Nickerson \cite{yu_cooks_2011}). Secondly, we piloted asking respondants for "as many ideas as possible" in a generous time frame. Over N respondents, we received a mean of N ideas (std N), despite giving a financial of \$\$\$\$. This suggested a propensity to "game the system", a behaviour we wanted to exclude.

We chose to focus on this problem because a) we expected workers to be familiar with problem area (old MP3 players), b) it represents a real-world problem for which innovative solutions are welcome (namely, what to do with old electronics that are still partially functional), and c) we anticipated there to be a wide range of creative solutions possible. All data presented in this paper refer only to responses received to this particular question.

Initially, workers were randomly paired with a question from a pool of questions. However, we eventually dropped all other questions, so workers would only receive the MP3 player question. When testing multiple questions, we attempted to prevent workers from answering the same question twice (for example, if they chose the HIT requesting 10 responses, then the HIT requesting 20 responses) . However, we were not always successful in preventing this from happening. Thus, we only use a worker's first set of responses if they answered the question multiple times.

%Because workers could choose which \emph{number of ideas} condition to participate in, self-selection bias is a reasonable concern. However, this bias is also present in real-world HIT choice behaviour.

\subsection{Worker's Brainstorming Interface}

Upon accepting a HIT, participants were asked to give consent for participating in the study, and informed that they could leave the study at any point without financial consequences. Under more realistic, real-world conditions, workers would be expected to complete all responses to receive compensation. As we will report later, the incidence of workers abusing this policy was relatively low.

The brainstorming task was presented in a standard web-based form that included an introduction, the specific brainstorming problem, a series of fields for entering the individual responses, and a larger text area where workers could enter additional ideas (TODO: Figure X).

The introduction Osborne's four rules of brainstorming \cite{osborn_applied_1957}, adapted to this context:

@@

In addition to the visible input fields, HITs were instrumented to collect timing data. Specifically, we recorded the time of the first activation and last de-activation of each form element, the time the HIT was accepted, and the time it was submitted.

\subsection{Data Collected}

Initially, we sought 10 HITs for each condition. However, we found that collecting only 10 HITs for the lower response conditions (5, 10, 20 responses) limited our ability to make meaningful comparisons between responses received from the larger response conditions (50, 75, 100). Accordingly, we sought to receive a minimum of 400 ideas for each condition. We found the 5 and 10 conditions to be particularly unpopular, and were not able to fully reach the desired number of ideas in these conditions.

In total, 154 workers submitted 170 HITs, for a total of 3292 responses. As we received data in the unlimited condition, it became obvious that this was a poor strategy to employ -- the number of responses received was less than 15 in all cases. Accordingly, we remove that data from our analysis.

If a worker completed multiple HITs (i.e., generated responses for multiple conditions), there is the risk their responses and idea generation processes evolved over time, making it difficult to compare their responses in the second HIT with responses from others who are performing the same HIT without any previous exposure to the problem. Accordingly, we retain only the first HIT submitted by the same worker.

After removing these data, we are left with 146 distinct participants for a total of 146 HITs, yielding 3007 responses. A breakdown of responses across conditions is given in table TODO: TAB.

@@

%To uniquely identify participants, we computed a hash of their Mechanical Turk worker ID. A hash was used to protect privacy after data release.

\subsection{Hierarchical Clustering}

To analyze the data, we organized it into sets hierarchical clusters, where the clusters encode similarity relationships between ideas. Specifically, parent nodes are more generalized versions of child nodes. This clustering enables a wide range of data analysis. We introduce specific terminology, then describe the clusters and the process used to create them.

\subsubsection{Clustering: Terminology}
An \emph{instance} is a single solution by a single participant to a brainstorming question. Most concretely, it is the text entered into a single field in the web form. For example, figure~\ref{fig:sample_instances} provides an example of four \emph{instances} from workers.

@@

A \emph{brainstorming run}, or \emph{run}, is the temporally-ordered series of instances that were received in a single HIT by a single worker.

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, though multiple instances can be associated with the same idea (i.e., when multiple workers come up with the same idea). Multiple instances of the same idea do not need to be identically phrased to refer to the same idea. For example, in Figure FIG, we consider ``Storage Container'' and ``Small Storage Box'' as two instances of the same \emph{idea}. However, we do not consider ``Coin Storage'' to be the same idea, since it provides a more specific use case than the previous two.

Despite the differences in specificity between ``Coin Storage'' and the more generic containers, it is useful to encode the fact that these ideas are related. We use hierarchical clustering to encode that relationship. We call a hierarchical cluster of ideas a \emph{category trees}.

In a category tree, ideas act as nodes. Each idea may optionally have a single parent idea, and zero or more child ideas. If an idea \emph{A} is a parent of idea \emph{B}, A is a generalization of B. An example category tree for the instances in Figure FIG is given in Figure FIG.

@@

Category trees can either be \emph{singletons} or \emph{non-singletons}. A singleton category tree is composed of only one \emph{idea node}, the root. A non-singleton category tree has \emph{at least two idea nodes}. Non-singleton category trees correspond to the ``images'' described in Nisjstad and Stroebe's SIAM model \cite{nijstad_how_2006}.

Finally, the \emph{idea forest} is the collection of all category trees.

\subsubsection{Clustering: Process}
To produce the idea forest, the primary author added instances to the idea forest one at a time using the following algorithm.

If an instance described an idea already represented as a node in the forest, the instance was added to that node. Otherwise, a new node was produced.

If a node was a generalization of a second node, the second node was introduced as a child of the first. In some cases, two ideas were clearly related, though no generalization of the two existed in the data set. In these cases, we introduced a node that is a generalization of the two. For example, if we received only ``Coin Storage'' and ``Travel Jewelry Case'' as ideas, we would create a node labeled ``Storage Case'' to capture the fact that the two are related concepts. These ``artificial'' nodes were marked to distinguish them from true generalizations found in the data.

Clustering was performed using a custom-built tool that assisted in finding instances that were similar to a given instance. Briefly, the tool represented each instance using a bag of words model which included synonyms for words. The words were stemmed, then individual instances were ranking according to a cosine similarity metric.

The primary author clustered the 3007 response instances into ideas and category trees. A researcher not involved in the project randomly sampled 40 category trees to assess whether ideas within the tree should be there, and whether parent-child relationships correctly encoded generalizations of concepts. Results indicate that 8\% of the data would be X by the independent researcher, and 0.7\% of the data would be Y by the independent researcher.

%In brief summary, the root idea that most closely matches the strategy in the instance is selected, and then that root idea and the new instance are compared in generality. This process may be repeated depending on this generality relationship, until instance is either placed in an existing idea or a new idea node is created.

% \begin{figure*}[ht]
% \small
% \begin{verbatim}
% for each instance:
%   idea_node = new node including instance
%   current_node = root of forest
%   do:
%     best_match = max_similarity(idea_node, current_node.children)

%     if best_match.similarity is low or current_node has no children:
%       insert idea_node under current_node
%       exit do
%     else:
%       if coverage(idea_node, best_match) == coverage(best_match, idea_node) == high:
%         merge idea_node, best_match
%         exit do
%       else if coverage(idea_node, best_match) == coverage(best_match, idea_node) == low:
%         new_parent = new artifical idea node
%         insert best_match, idea_node under new_parent
%         insert new_parent under current_node
%         exit do
%       else if coverage(idea_node, best_match) > coverage(best_match, idea_node):
%         replace best_match with idea_node in tree
%         current_node = idea_node
%         idea_node = best_match
%       else:
%         current_node = best_match
% \end{verbatim}
% \caption{Manual clustering algorithm}
% \label{fig:cluseringalg}
% \end{figure*}
